---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ohwhaley

Whale-come! This R package was inspired by [cowsay](https://github.com/sckott/cowsay) and [praise](https://github.com/rladies/praise). I hope this package made you smile today! 

## First things first

`ohwhaley` is a toy project and is still under development. You can install the latest version from [GitHub](https://github.com/) with:

```{r, install, results = "hide", eval = FALSE}
# install.packages("remotes")
remotes::install_github("CaitlinLuo/ohwhaley")
```

## Take it for a spin

`ohwhaley` contains only one function only. `say()` will echo a randomly
chosen whale-themed phrase for your enjoyment.

```{r example}
library(ohwhaley)

say()
```

Alternatively, you can supply your own phrase

```{r, customise}
say("I`m beached bro!!!")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
